Verifying Demonstrations

### 2018-08-30 paper/DB-anon-cred.tex

We present the protocol in \cref{SchnorrFigure}.
The main difference to the original Schnorr protocol is that the prover commits 
to one random value but the verifier sends \emph{two challenges}.
This is also different from Brands-Chaum, where the prover and verifier jointly 
construct the challenge.
(We let \(|q| = \ceil{\log_2 q}\) denote the length of \(q\) in bits.)
The verifier will request all \(|q|\) response-bits from one challenge and only 
\(l > 0\) from the other.
The prover must know the responses for both challenges to successfully pass the 
\ac{DB} phase.

@@

Finally, a malicious verifier who wants to impersonate a prover can guess the 
remaining \(|q|-l\) bits after the protocol finished to compute the secret of 
the prover.
The probability that this succeeds is, as above, \(2^{-(|q|-l)}\).

>>>>

We present the protocol in \cref{SchnorrFigure}.
The main difference to the original Schnorr protocol is that the prover commits 
to one random value but the verifier sends \emph{two challenges}.
This is also different from Brands-Chaum, where the prover and verifier jointly 
construct the challenge.
(We let \(|q| = \ceil{\log_2 q}\) denote the length of \(q\) in bits.)
The verifier will request all \(|q|\) response-bits from one challenge and only 
\(l > 0\) from the other.
The prover must know the responses for both challenges to successfully pass the 
\ac{DB} phase.
The reason for the two challenges (change from Schnorr) is that
knowing the responses to both means learning $\alpha$ (for
\ac{DBTF}). Bundling the authentication into the distance bounding
phase (additional change from Brands-Chaum) was done for \ac{DBDH},
and both adaptations together aim at \ac{DBMF} resistance. %reducing success of MF according to number of repetitions.

@@

\ac{DBIF} resistance follows from Schnorr.\sonja{Daniel, please
  complete this sentence:, our changes don't break Schnorr because ...}
Finally, a malicious verifier who wants to impersonate a prover can guess the 
remaining \(|q|-l\) bits after the protocol finished to compute the secret of 
the prover.
The probability that this succeeds is, as above,
\(2^{-(|q|-l)}\). While the majority of \ac{DB} schemes are based on
shared secrets and thus assume an honest verifier, this limits the
inherent advantage of our public-key
\ac{DB} scheme.

### 2018-08-30 paper/intro.tex

Historically, there are many examples of protests in which the count estimated by police and that by the organizers differ significantly, sometimes in the order of hundreds of thousands.
Even without foul play, the difference is quite natural as both parties have different objectives and metrics.
More precisely, the organizers want to count everyone who participated while the police want to estimate the count at the peak of participation, due to crowd control~\cite{2016DemonstrationsInSeoul}.
Among the numerous recent examples in which it is difficult to establish the actual number of participants, there are the demonstrations against the president in South Korea~\cite{2016DemonstrationsInSeoul}, Trump's inauguration attendance~\cite{HowWillWeKnowTrumpInauguralCrowdSize}, the 2017 Women's March in the US~\cite{2017WomensMarchesInUS}, the demonstrations against the change of constitution in Venezuela~\cite{AlJazeeraOnVenezuela2017} or for the independence of Catalonia~\cite{CataloniaDemonstrations}.

@@

Our second contribution is an adaptation of the Schnorr protocol~\cite{Schnorr} 
for \ac{DB}, but which is different from that of \textcite{DistanceBounding}.
Our adaptation fulfills all the requirements for modern \ac{DB} protocols, including \ac{DBDH} (which was an attack against Brands-Chaum).
More importantly, it is public-key, handles malicious impersonating verifiers, fulfills \ac{DBTF} and other types of resistance (see \cref{distance-bounding}), and provides a \ac{PK} for discrete logarithms.
The latter allows us to replace the use of the plain Schnorr protocol in the \ac{ZKPK} used in anonymous credentials.
\seb{once again I think it is too strong to say that are the first to provide distance-bounding anonymous credentials as a a distance-bounding anonymous protocol can already be considered an anonymous credential in the sense that it allows to authenticate anonymously in addition of providing proximity testing
%and thus we are, to the best of our knowledge, the first to provide \ac{DB} anonymous credentials.
}
\emph{Outline.} 
The paper is organized as follows.
First, in \cref{system-model}, we define and formalize the notion of protest 
and define the desired verifiability properties.
We also present our system and adversary model together with desired privacy 
properties.
Next, in \cref{related-work}, we discuss related work in terms of these 
properties.
In \cref{building-blocks}, we give the relevant background on the building 
blocks of our solution.
In \cref{DB-anon-cred}, we present a new \ac{DB} version of the Schnorr 
protocol, different from that originally proposed by 
\textcite{DistanceBounding}.
We provide a proof of its security (all desired \ac{DB} properties) 
\daniel{Check that this is true before publication.} and formally verify it 
using Tamarin~\cite{TamarinDB}.
This version of the Schnorr protocol can then be used to do general \ac{DB} 
anonymous credentials.
In \cref{Protocol}, we present \PRIVO, the protocol constructed from these 
building blocks.
This is followed by an analysis of its security and privacy 
(\cref{SecurityAnalysis}).
Finally, we conclude with a discussion in \cref{Discussion} and future work in 
\cref{Conclusion}.

>>>>

Historically, there are many examples of protests in which the count estimated by police and that by the organizers differ significantly, sometimes in the order of hundreds of thousands.
Even without foul play, the difference is quite natural as both parties have different objectives and metrics.
More precisely, the organizers want to count everyone who participated while the police want to estimate the count at the peak of participation, due to crowd control~\cite{2016DemonstrationsInSeoul}.
Among the numerous recent examples in which it is difficult to establish the actual number of participants, there are the demonstrations against the president in South Korea~\cite{2016DemonstrationsInSeoul}, Trump's inauguration~\cite{HowWillWeKnowTrumpInauguralCrowdSize}, the 2017 Women's March in the US~\cite{2017WomensMarchesInUS}, the demonstrations against the change of constitution in Venezuela~\cite{AlJazeeraOnVenezuela2017} or for the independence of Catalonia~\cite{CataloniaDemonstrations}.

@@

Our second contribution is an adaptation of the Schnorr protocol~\cite{Schnorr} 
for \ac{DB}, but which is different from that of \textcite{DistanceBounding}.
Our adaptation fulfills all the requirements for modern \ac{DB} protocols, including \ac{DBDH} (which was an attack against Brands-Chaum).
More importantly, it is public-key, handles malicious impersonating verifiers, fulfills \ac{DBTF} and other types of resistance (see \cref{distance-bounding}), and provides a \ac{PK} for discrete logarithms.
The latter allows us to replace the use of the plain Schnorr protocol in the \ac{ZKPK} used in anonymous credentials.
\seb{once again I think it is too strong to say that are the first to provide distance-bounding anonymous credentials as a a distance-bounding anonymous protocol can already be considered an anonymous credential in the sense that it allows to authenticate anonymously in addition of providing proximity testing
%and thus we are, to the best of our knowledge, the first to provide \ac{DB} anonymous credentials.
}
\sonja{Daniel, can you contrast that with the other DB AC approaches, what are they not general enough for, or what can we do they can't?}
and thus we are, to the best of our knowledge, the first to provide \emph{general} \ac{DB} anonymous credentials.
\emph{Outline.} 
The paper is organized as follows.
First, in \cref{system-model}, we define and formalize the notion of protest 
and define the desired verifiability properties.
We also present our system and adversary model together with desired privacy 
properties.
Next, in \cref{related-work}, we discuss related work in terms of these 
properties.
In \cref{building-blocks}, we give the relevant background on the building 
blocks of our solution.
In \cref{DB-anon-cred}, we present a new \ac{DB} version of the Schnorr 
protocol, different from that originally proposed by 
\textcite{DistanceBounding}.
We provide a proof of its security (all desired \ac{DB} properties) 
\daniel{Check that this is true before publication.} and formally verify it 
using Tamarin~\cite{TamarinDB}.
This version of the Schnorr protocol can then be used to do general \ac{DB} 
anonymous credentials.
In \cref{Protocol}, we present \PRIVO, the protocol constructed from these 
building blocks.
This is followed by an analysis of its security and privacy 
(\cref{SecurityAnalysis}).
Finally, we conclude with a discussion in \cref{Discussion} and future work in 
\cref{Conclusion}.
\sonja{add (sub) sections for performance and verification}

### 2018-08-30 paper/protest-model.tex
Merges protest model and security properties into system model

\section{Defining and formalizing protest and crowd estimation}%
\label{SystemModel}

@@

%\emph{Defining the concept of protest.} 
To be able to estimate the participation count for a protest, we first need to define this concept and which quantity should be counted.
Let us start by considering some examples.
During the demonstrations against the South Korean president in Seoul in 2016
\blockcquote{2016DemonstrationsInSeoul}{%
  \textins*{t}he rallies stretch\textins{ed} from midday to late night --- some people stay\textins{ed} for several hours, others just several minutes%
}.
These rallies were all in the same location in the capital city and repeated every weekend for the duration of a few weeks.
The Women's Marches in 2017~\cite{2017WomensMarchesInUS}, on the other hand, occurred in parallel in many locations.
We also have the Venezuelan demonstrations in 2017 in which \blockcquote{2017VenezuelaProtestFrequency}{%
  anti-government demonstrators have staged daily protests across Venezuela%
} while
\blockcquote{AlJazeeraOnVenezuela2017}{%
  pro-government workers sang and danced as they staged a rival march to show their support for the president's controversial plan to rewrite the constitution%
}.
Generalizing from these examples, the minimal common part is the cause,%
\label{CauseIsTheCommonDenominator} while the location (or area) considered 
varies over time.

For the rest of the paper, we will refer to the organizer as Alice.
Assume that the objective of Alice is to count everyone who
participated at any time and in any of the
locations~\cite{2016DemonstrationsInSeoul} \sonja{commented out for
  repetition: %\footnote{Note that the objective does not necessarily
              %align with the definition of the police whose interest
              %could be to determine the maximum crowd at any point in
              %time to deploy enough personnel for crowd-control.
}.
% cause identifier
Formally, we define a protest as an event that is uniquely identified by its cause \(\cid\), its time interval \(t\) and its location (area) \(l\).
More specifically, we will use the following definition.

@@

The protests described in the previous examples can be captured using this definition by decomposing them up into subprotests.
Each subprotest will then be encapsulated by our definition and to estimate the total participation to the protest we can just sum up the estimates obtained.
Similarly for marches, the marching path can be divided into subprotests with locations (or areas) that slightly overlap.

\emph{Formalizing the notion of crowd estimation.} 
Each participant who wants to be counted must submit a \emph{participation proof}.
The proof must be associated with the protest (\ie its identifier \(cid\)), and its time and location must coincide with one of the subprotests.

Our protocol relies on \emph{witnesses} to certify and associate the proof to the location by creating a \emph{proof share}.
A witness is only allowed to create one proof share per protester to avoid the risk of inflation.
Note that a participant of a protest can take the role of a protester but also act as witness for other protesters.
%Seb: the sentence below is not very clear, it should be rephrased to make it clearer
The participation proof and its proof shares are stored in a set, as there should be only unique proof shares.

@@

% proof
% proofs

\begin{definition}[Participation proof]%
  \label{DefParticipationProof}\label{DefParticipationProofs}
  A \emph{participation proof} of a protester with pseudonym \(\pid\) who participates in a protest \(\prtst = \{ (\cid, t_i, l_i) \}_i\) is the set
  \begin{multline}
    \nonumber
    \prf_{\pid, \prtst} =
    \left\{ \psh = (\cid, t, l, \pid, \wid)\in \pshs \mid
      \exists \sprtst\in \prtst\colon \psh\sqsubseteq \sprtst \right\}
  \end{multline}
  of all proof shares with the same protester and protest identifiers, witnessing time interval \(t\) and location \(l\) within those of the protest.
  We denote by \(\prfs\) the set of all proofs.
\end{definition}

>>>>

\subsection{Defining and formalizing protest and crowd estimation}%
\label{protest-model}

@@

%\emph{Defining the concept of protest.} 
To be able to estimate the participation count for a protest, we first need to define this concept and which quantity should be counted.
Let us start by considering some examples.
During the demonstrations against the South Korean president in Seoul in 2016
\blockcquote{2016DemonstrationsInSeoul}{%
  \textins*{t}he rallies stretch\textins{ed} from midday to late night --- some people stay\textins{ed} for several hours, others just several minutes%
}.
These rallies were all in the same location in the capital and repeated every weekend for the duration of a few weeks.
The Women's Marches in 2017~\cite{2017WomensMarchesInUS}, on the other hand, occurred in parallel in many locations.
We also have the Venezuelan demonstrations in 2017 in which \blockcquote{2017VenezuelaProtestFrequency}{%
  anti-government demonstrators have staged daily protests across Venezuela%
} while
\blockcquote{AlJazeeraOnVenezuela2017}{%
  pro-government workers sang and danced as they staged a rival march to show their support for the president's controversial plan to rewrite the constitution%
}.
Generalizing from these examples, the minimal common part is the cause,%
\label{CauseIsTheCommonDenominator} while the location (or area) considered 
varies over time.

For the rest of the paper, we will refer to the organizer as Alice.
Assume that the objective of Alice is to count everyone who
participated at any time and in any of the
locations~\cite{2016DemonstrationsInSeoul} %\sonja{commented out for
  %repetition: %\footnote{Note that the objective does not necessarily
              %align with the definition of the police whose interest
              %could be to determine the maximum crowd at any point in
              %time to deploy enough personnel for crowd-control.
%}.
% cause identifier
Formally, we define a protest as an event that is uniquely identified by its cause \(\cid\), its time interval \(t\) and its location (area) \(l\).
More specifically, we will use the following definition.

@@

The protests described in the previous examples can be captured using this definition by decomposing them into subprotests.
Each subprotest will then be encapsulated by our definition and to estimate the total participation to the protest we can just sum up the estimates obtained.
Similarly for marches, the marching path can be divided into subprotests with locations (or areas) that slightly overlap.

\emph{Formalizing the notion of crowd estimation.} 
Each participant who wants to be counted must submit a \emph{participation proof}.
The proof must be associated with the protest (\ie its cause identifier \(cid\)), and its time and location must coincide with one of the subprotests.

Our protocol relies on \emph{witnesses} to certify and associate the proof to the location by creating a \emph{proof share}.
A witness is only allowed to create one proof share per protester to
avoid the risk of count inflation.
Note that a participant of a protest can take the role of a protester but also act as witness for other protesters.
%Seb: the sentence below is not very clear, it should be rephrased to make it clearer
The participation proof and its proof shares are stored in a set, as
there should only be unique proof shares.

@@

% proof
% proofs
\sonja{what is the subscript i and do we need to have it here?}
\begin{definition}[Participation proof]%
  \label{DefParticipationProof}\label{DefParticipationProofs}
  A \emph{participation proof} of a protester with pseudonym \(\pid\) who participates in a protest \(\prtst = \{ (\cid, t_i, l_i) \}_i\) is the set
  \begin{multline}
    \nonumber
    \prf_{\pid, \prtst} =
    \left\{ \psh = (\cid, t, l, \pid, \wid)\in \pshs \mid
      \exists \sprtst\in \prtst\colon \psh\sqsubseteq \sprtst \right\}
  \end{multline}
  of all proof shares with the same protester and protest identifiers, witnessing time interval \(t\) and location \(l\) within those of the protest.
  We denote by \(\prfs\) the set of all proofs.
\end{definition}

### 2018-08-30 paper/verifiability-properties.tex

To define these properties more in the context of protests, we define three 
verifiability requirements, among which eligibility can be further broken up 
into four subproperties:
\begin{requirements}[V]
  \item\label{EligibilityVerif} \emph{Eligibility}: anyone can verify that each participation proof provides temporal and spatial eligibility and that only one participation proof is counted per individual.
    \begin{requirements}
    \item\label{TemporallyRelated} \emph{Temporal eligibility}: prove that the proof was created after the start of the protest and before the end of the protest.
    \item\label{SpatiallyRelated} \emph{Spatial eligibility}: prove that the proof is spatially related to the physical location or journey of the protest.
    \item\label{CountOnce} \emph{One-proof-per-person}: prove that no individual can be counted more than once for a particular protest.
    \item\label{DesignatedEvent} \emph{Designated event}: prove that the proof is associated to particular designated protest.
    \end{requirements}

>>>>

To adapt these properties to the context of protests, we define three 
verifiability requirements, among which eligibility can be further broken up 
into four subproperties:
\begin{requirements}[V]
  \item\label{EligibilityVerif} \emph{Eligibility}: anyone can verify that each participation proof provides temporal and spatial eligibility and that only one participation proof is counted per individual.
    \begin{requirements}
    \item\label{TemporallyRelated} \emph{Temporal eligibility}: prove that the proof was created after the start of the protest and before the end of the protest.
    \item\label{SpatiallyRelated} \emph{Spatial eligibility}: prove that the proof is spatially related to the physical location or journey of the protest.
    \item\label{CountOnce} \emph{One-proof-per-person}: prove that no individual can be counted more than once for a particular protest.
    \item\label{DesignatedEvent} \emph{Designated event}: prove that the proof is associated with particular designated protest.
    \end{requirements}
